---
title: "Puget Sound Larvae Growth"
author: "Katherine Silliman"
output:
  github_document:
    toc: yes
  html_notebook:
    fig_height: 3
    fig_width: 4
---

References
http://www.flutterbys.com.au/stats/tut/tut9.2a.html
http://rcompanion.org/rcompanion/d_07.html

```{r, message=FALSE}
library(dplyr) #data frame grouping
library(nlme) #LMMs, using likelihood ratio test for significance
library(plotrix)#for SE calculation
#library(multcompView)
library(ggplot2)
library(lme4) #for linear mixed models
library(afex) #different way for getting significance from LMMs
library(PMCMR) #Kruskal-Wallis test
```
# Setting up
Reading in larvae size data.
```{r}
all.larvae <- read.csv("PS_Larvae.csv",header = TRUE, na.strings = "#DIV/0!")
G1.all <- select(all.larvae, Population, Replicate, Date, Average_Length,Area) %>% group_by(Population,Date)
```
Summarizing sizes at different time points.
```{r}
G1.all.mean <- summarise(G1.all,mean.Area = mean(Area, na.rm = T),se.Area = std.error(Area,na.rm =T),mean.Length = mean(Average_Length, na.rm = T),se.Length = std.error(Average_Length,na.rm =T))
G1.all.mean
```
# Day 1
Plotting size distributions at Day 1.
```{r}
p.Day1 <- ggplot(filter(G1.all,Date == "7-1-15"), aes(x=Population, y=Area,fill=Population)) + 
  geom_violin(trim=FALSE) + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) + geom_boxplot(width=0.1,fill="white") + labs(title="Area Day 1",y="Area (mm^2)")
p.Day1

p.Day1.L <- ggplot(filter(G1.all,Date == "7-1-15"), aes(x=Population, y=Average_Length,fill=Population)) + 
  geom_violin(trim=FALSE) + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) + geom_boxplot(width=0.1,fill="white") + labs(title="Length Day 1",y="Length (mm)")
p.Day1.L
```
Checking for normal distributions in Area at each time point.
```{r}
plot(density(filter(G1.all,Date=="7-1-15",Population=="SS")$Area,na.rm = T),col="#56B4E9", main ="Day 1 distributions")
lines(density(filter(G1.all,Date=="7-1-15",Population=="HC")$Area,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-1-15",Population=="NF")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-1-15",Population=="SS")$Area)
shapiro.test(filter(G1.all,Date=="7-1-15",Population=="HC")$Area)
shapiro.test(filter(G1.all,Date=="7-1-15",Population=="NF")$Area)

plot(density(filter(G1.all,Date=="7-8-15",Population=="SS")$Area,na.rm = T),col="#56B4E9", main ="Day 7 distributions",xlim=c(0.009,0.03),ylim=c(0,200))
lines(density(filter(G1.all,Date=="7-8-15",Population=="HC")$Area,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-8-15",Population=="NF")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-8-15",Population=="SS")$Area)
shapiro.test(filter(G1.all,Date=="7-8-15",Population=="HC")$Area)
shapiro.test(filter(G1.all,Date=="7-8-15",Population=="NF")$Area)

plot(density(filter(G1.all,Date=="7-15-15",Population=="SS")$Area,na.rm = T),col="#56B4E9", main ="Day 14 distributions",xlim =c(0.009,0.045))
lines(density(filter(G1.all,Date=="7-15-15",Population=="HC")$Area,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-15-15",Population=="NF")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-15-15",Population=="SS")$Area)
shapiro.test(filter(G1.all,Date=="7-15-15",Population=="HC")$Area)
shapiro.test(filter(G1.all,Date=="7-15-15",Population=="NF")$Area)
```
Shell area in SS and NF at Day 14 does not have a normal distribution. 

Checking for normal distributions in Length at each time point.
```{r}
plot(density(filter(G1.all,Date=="7-1-15",Population=="SS")$Average_Length,na.rm = T),col="#56B4E9", main ="Day 1 distributions", xlim=c(0.11,0.19))
lines(density(filter(G1.all,Date=="7-1-15",Population=="HC")$Average_Length,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-1-15",Population=="NF")$Average_Length,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-1-15",Population=="SS")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-1-15",Population=="HC")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-1-15",Population=="NF")$Average_Length)

plot(density(filter(G1.all,Date=="7-8-15",Population=="SS")$Average_Length,na.rm = T),col="#56B4E9", main ="Day 7 distributions",xlim=c(0.12,0.21),ylim=c(0,50))
lines(density(filter(G1.all,Date=="7-8-15",Population=="HC")$Average_Length,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-8-15",Population=="NF")$Average_Length,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-8-15",Population=="SS")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-8-15",Population=="HC")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-8-15",Population=="NF")$Average_Length)

plot(density(filter(G1.all,Date=="7-15-15",Population=="SS")$Average_Length,na.rm = T),col="#56B4E9",main ="Day 14 distributions",xlim =c(0.12,0.25))
lines(density(filter(G1.all,Date=="7-15-15",Population=="HC")$Average_Length,na.rm = T),col="#999999")
lines(density(filter(G1.all,Date=="7-15-15",Population=="NF")$Average_Length,na.rm = T),col="#E69F00")

shapiro.test(filter(G1.all,Date=="7-15-15",Population=="SS")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-15-15",Population=="HC")$Average_Length)
shapiro.test(filter(G1.all,Date=="7-15-15",Population=="NF")$Average_Length)
```
# Plotting Size through time
```{r}
G1.all.mean$Date <- c(1,14,7,1,14,7,1,14,7)
Fig.Area <- ggplot(G1.all.mean, aes(x=Date, y=mean.Area, group=Population)) +
  geom_errorbar(aes(ymin=G1.all.mean$mean.Area-G1.all.mean$se.Area,ymax=G1.all.mean$mean.Area+G1.all.mean$se.Area,color=Population), width=.07) +
  geom_line(aes(color=Population) ,size = 0.5) +   
  geom_point(aes(shape=Population,color=Population), size = 3)+
  xlab("Days") +scale_x_continuous(breaks=c(1,7,14))+
  ylab(expression(paste("Shell Area (mm^2)"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Larvae Shell Area") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.Area <- Fig.Area + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
Fig.Area

Fig.L <- ggplot(G1.all.mean, aes(x=Date, y=mean.Length, group=Population)) +
  geom_errorbar(aes(ymin=G1.all.mean$mean.Length-G1.all.mean$se.Length,ymax=G1.all.mean$mean.Length+G1.all.mean$se.Length,color=Population), width=.07) +
  geom_line(aes(color=Population) ,size = 0.5) +   
  geom_point(aes(shape=Population,color=Population), size = 3)+
  xlab("Days") +scale_x_continuous(breaks=c(1,7,14))+
  ylab(expression(paste("Shell Area (mm)"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Larvae Shell Length") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.L <- Fig.L + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
Fig.L
```
# Testing for differences in size
ANOVA of size at Day 1 to test if size differs accross populations at Day 1
```{r}
G1.D1 <- filter(G1.all, Date == "7-1-15")
area.D1 <- aov(Area ~ Population, data=G1.D1) #test the hypothesis relative size does not differ between treatments on Day 1
area.D1.res <- anova(area.D1)
area.D1.res

length.D1 <- aov(Average_Length ~ Population, data=G1.D1) #test the hypothesis relative size does not differ between treatments on Day 1
length.D1.res <- anova(length.D1)
length.D1.res
```
## Day 7
Untransformed shell area.
```{r}
G1.D7 <- filter(G1.all, Date == "7-8-15")
area.D7.model = lmer(Area ~ Population + (1|Replicate),data=G1.D7,na.action = na.omit)
summary(area.D7.model)
area.null <- lmer(Area ~ (1|Replicate),data=G1.D7,REML=FALSE)
area.model.R <- lmer(Area ~ Population + (1|Replicate),data=G1.D7,REML = F)
anova(area.null,area.model.R)

afex.1 <- mixed(Area ~ Population + (1|Replicate), data=G1.D7,na.action = na.omit)
print(afex.1)
```
Log-transformed shell area.
```{r}
Larea.D7.model = lmer(log10(Area) ~ Population + (1|Replicate),data=G1.D7,na.action = na.omit)
summary(Larea.D7.model)
area.null <- lmer(log10(Area) ~ (1|Replicate),data=G1.D7,REML=FALSE)
area.model.R <- lmer(log10(Area) ~ Population + (1|Replicate),data=G1.D7,REML = F)
anova(area.null,area.model.R)

afex.1 <- mixed(log10(Area) ~ Population + (1|Replicate), data=G1.D7,na.action = na.omit)
print(afex.1)
```
Untransformed shell length, Day 7.
```{r}
length.D7.model = lmer(Average_Length ~ Population + (1|Replicate),data=G1.D7,na.action = na.omit)
summary(length.D7.model)
area.null <- lmer(Average_Length ~ (1|Replicate),data=G1.D7,REML=FALSE)
area.model.R <- lmer(Average_Length ~ Population + (1|Replicate),data=G1.D7,REML = F)
anova(area.null,area.model.R)
afex.1 <- mixed(Average_Length ~ Population + (1|Replicate), data=G1.D7,na.action = na.omit)
print(afex.1)
```
Log-transformed shell length, Day 7.
```{r}
Larea.D7.model = lmer(log10(Average_Length) ~ Population + (1|Replicate),data=G1.D7,na.action = na.omit)
summary(Larea.D7.model)
area.null <- lmer(log10(Average_Length) ~ (1|Replicate),data=G1.D7,REML=FALSE)
area.model.R <- lmer(log10(Average_Length) ~ Population + (1|Replicate),data=G1.D7,REML = F)
anova(area.null,area.model.R)

afex.1 <- mixed(log10(Average_Length) ~ Population + (1|Replicate), data=G1.D7,na.action = na.omit)
print(afex.1)
```

## Day 14
Untransformed Day 14 shell area
```{r}
G1.D14 <- filter(G1.all, Date == "7-15-15")
relarea.D14.model = lmer(Area ~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
summary(relarea.D14.model)
relarea.null <- lmer(Area ~ (1|Replicate),data=G1.D14,REML=FALSE)
relarea.model.R <- lmer(Area ~ Population + (1|Replicate),data=G1.D14,REML = FALSE)
anova(relarea.null,relarea.model.R)

afex.1 <- mixed(Area ~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
print(afex.1)
```
Log-transformed shell area, Day 14.
```{r}
Lrelarea.D14.model = lmer(log10(Area) ~ Population + (1|Replicate),data=G1.D14,na.action = na.omit)
summary(Lrelarea.D14.model)
relarea.null <- lmer(log10(Area) ~ (1|Replicate),data=G1.D14,REML=FALSE)
relarea.model.R <- lmer(log10(Area) ~ Population + (1|Replicate),data=G1.D14,REML = FALSE)
anova(relarea.null,relarea.model.R)

afex.1 <- mixed(log10(Area) ~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
print(afex.1)
```

Day 14 untransformed shell length:
```{r}
G1.D14 <- filter(G1.all, Date == "7-15-15")
relarea.D14.model = lmer(Average_Length ~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
summary(relarea.D14.model)
relarea.null <- lmer(Average_Length ~ (1|Replicate),data=G1.D14,REML=FALSE)
relarea.model.R <- lmer(Average_Length ~ Population + (1|Replicate), data=G1.D14,REML = FALSE)
anova(relarea.null,relarea.model.R)

afex.1 <- mixed(Average_Length~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
print(afex.1)
```
Log-transformed shell length, Day 14.
```{r}
Lrelarea.D14.model = lmer(log10(Average_Length) ~ Population + (1|Replicate),data=G1.D14,na.action = na.omit)
summary(Lrelarea.D14.model)
relarea.null <- lmer(log10(Average_Length) ~ (1|Replicate),data=G1.D14,REML=FALSE)
relarea.model.R <- lmer(log10(Average_Length) ~ Population + (1|Replicate),data=G1.D14,REML = FALSE)
anova(relarea.null,relarea.model.R)

afex.1 <- mixed(log10(Average_Length)~ Population + (1|Replicate), data=G1.D14,na.action = na.omit)
print(afex.1)
```

Kruskal-Wallis tests with Nemenyi post-hoc tests. Used when data is non-normal, which only occured in Day 14 shell area.
```{r}
#Shell area
posthoc.kruskal.nemenyi.test(G1.D1$Area,as.factor(G1.D1$Population),dist="Chisquare")
posthoc.kruskal.nemenyi.test(G1.D7$Area,as.factor(G1.D7$Population),dist="Chisquare")
posthoc.kruskal.nemenyi.test(G1.D14$Area,as.factor(G1.D14$Population),dist="Chisquare")
```
Pairwise t-test with bonferroni correction. Only appropriate for Day 1 and Day 7
```{r}
pairwise.t.test(G1.D1$Area,G1.D1$Population,p.adjust.method = "bonferroni")
pairwise.t.test(G1.D7$Area,G1.D7$Population,p.adjust.method = "bonferroni")
pairwise.t.test(G1.D14$Area,G1.D14$Population,p.adjust.method = "bonferroni")
```
Shell Length tests
```{r}
posthoc.kruskal.nemenyi.test(G1.D1$Average_Length,as.factor(G1.D1$Population),dist="Chisquare")
posthoc.kruskal.nemenyi.test(G1.D7$Average_Length,as.factor(G1.D7$Population),dist="Chisquare")
posthoc.kruskal.nemenyi.test(G1.D14$Average_Length,as.factor(G1.D14$Population),dist="Chisquare")
```
```{r}
pairwise.t.test(G1.D1$Average_Length,G1.D1$Population,p.adjust.method = "bonferroni")
pairwise.t.test(G1.D7$Average_Length,G1.D7$Population,p.adjust.method = "bonferroni")
pairwise.t.test(G1.D14$Average_Length,G1.D14$Population,p.adjust.method = "bonferroni")
```
# Using Relative Area and Length
Calculating shell area means at Day 1 for normalizations. This could be used is shell size varied significantly at Day 1. We did not observe this, but size did differ slightly between HC and NF/SS. 
```{r}
means.A <- summarise(G1.all, mean.area = mean(Area, na.rm = TRUE), mean.length = mean(Average_Length))
mean.A.HC <- subset(means.A,Population =="HC" &Date=="7-1-15",select=mean.area) #subset mean area for day 1 HC
mean.A.SS <- subset(means.A,Population =="SS"&Date=="7-1-15",select=mean.area) #subset mean area for day 1 SS
mean.A.NF <- subset(means.A,Population =="NF"&Date=="7-1-15",select=mean.area) #subset mean area for day 1 NF

mean.L.HC <- subset(means.A,Population =="HC" &Date=="7-1-15",select=mean.length) #subset mean area for day 1 HC
mean.L.SS <- subset(means.A,Population =="SS"&Date=="7-1-15",select=mean.length) #subset mean area for day 1 SS
mean.L.NF <- subset(means.A,Population =="NF"&Date=="7-1-15",select=mean.length) #subset mean area for day 1 NF
```
```{r}
A.norms <- function(x) {  #write function
  if(x == "HC") y <- mean.A.HC #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  if(x == "SS") y <- mean.A.SS #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  if(x == "NF") y <- mean.A.NF #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  return(y) #return result
}
L.norms <- function(x) {  #write function
  if(x == "HC") y <- mean.L.HC #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  if(x == "SS") y <- mean.L.SS #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  if(x == "NF") y <- mean.L.NF #if Treatment equals Ambient assign day 1 Ambient mean as normalization factor
  return(y) #return result
}
G1.all$A.norm <- as.numeric(sapply(G1.all$Population,A.norms))
G1.all$L.norm <- as.numeric(sapply(G1.all$Population,L.norms))
G1.all$A.rel <- G1.all$Area /G1.all$A.norm #normalize the area to be relative size
G1.all$L.rel <- G1.all$Average_Length /G1.all$L.norm #normalize the area to be relative size
```
Summarizing:
```{r}
Area.Size <- summarise(G1.all,mean.RelArea = mean(A.rel),se.RelArea = std.error(A.rel,na.rm =T),mean.RelLength = mean(L.rel, na.rm = T),se.RelLength = std.error(L.rel,na.rm =T))
Area.Size
```
```{r}
Area.Size$Date <- c(1,14,7,1,14,7,1,14,7)
Fig.Area.size <- ggplot(Area.Size, aes(x=Date, y=mean.RelArea, group=Population)) + 
  geom_errorbar(aes(ymin=Area.Size$mean.RelArea-Area.Size$se.RelArea,ymax=Area.Size$mean.RelArea+Area.Size$se.RelArea,color=Population), width=.07) +
  geom_line(aes(color=Population) ,size = 0.5) +   
  geom_point(aes(shape=Population,color=Population), size = 3)+
  xlab("Days") +scale_x_continuous(breaks=c(1,7,14))+
  ylab(expression(paste("Relative Shell Area"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Larvae Relative Shell Area") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.Area.size + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))

Area.Size$Date <- c(1,14,7,1,14,7,1,14,7)
Fig.Length.size <- ggplot(Area.Size, aes(x=Date, y=mean.RelLength, group=Population)) + 
  geom_errorbar(aes(ymin=Area.Size$mean.RelLength-Area.Size$se.RelLength,ymax=Area.Size$mean.RelLength+Area.Size$se.RelLength,color=Population), width=.07,position = position_dodge(width = 0.1)) +
  geom_line(aes(color=Population) ,size = 0.5,position = position_dodge(width = 0.1)) +   
  geom_point(aes(shape=Population,color=Population), size = 3,position = position_dodge(width = 0.1))+
  xlab("Days") +scale_x_continuous(breaks=c(1,7,14))+
  ylab(expression(paste("Relative Shell Length"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Larvae Relative Shell Length") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.Length.size + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
```
Day 7 area
```{r}
G1.D7 <- filter(G1.all, Date == "7-8-15")
relarea.D7.model = lmer(A.rel ~ Population + (1|Replicate),data=G1.D7,na.action = na.omit)
summary(relarea.D7.model)
relarea.null <- lmer(A.rel ~ (1|Replicate),data=G1.D7,REML=FALSE)
relarea.model.R <- lmer(A.rel ~ Population + (1|Replicate),data=G1.D7,REML = F)
anova(relarea.null,relarea.model.R)
```
Day 14 area
```{r}
G1.D14 <- filter(G1.all, Date == "7-15-15")
relarea.D14.model = lmer(A.rel ~ Population + (1|Replicate),data=G1.D14,na.action = na.omit)
summary(relarea.D14.model)
relarea.null <- lmer(A.rel ~ (1|Replicate),data=G1.D14,REML=FALSE)
relarea.model.R <- lmer(A.rel ~ Population + (1|Replicate),data=G1.D14,REML = FALSE)
anova(relarea.null,relarea.model.R)
```

```{r}
posthoc.kruskal.nemenyi.test(G1.D7$A.rel,as.factor(G1.D7$Population),dist="Chisquare")
posthoc.kruskal.nemenyi.test(G1.D14$A.rel,as.factor(G1.D14$Population),dist="Chisquare")
```
