---
title: "Puget Sound Juvenile Growth"
author: "Katherine Silliman"
output:
  github_document:
    toc: yes
  html_notebook:
    fig_height: 3
    fig_width: 4
---
# Setting up
```{r, message=FALSE}
library(dplyr) #data frame grouping
library(nlme) #LMMs, using likelihood ratio test for significance
library(plotrix)#for SE calculation
#library(multcompView)
library(ggplot2)
library(lme4) #for linear mixed models
library(afex) #different way for getting significance from LMMs
library(PMCMR) #Kruskal-Wallis test
```
Reading in file with measurements, generated in Google Sheets.
```{r}
all.tiles <- read.csv("../../Data/Oyster Tile Size Data.csv",header = TRUE, na.strings = c("#DIV/0!","#VALUE!","e","gone","g","#NUM!","#REF!"))
```
Filter out oysters from B experiment, which were started 2 weeks later and had significantly higher mortality. 
```{r}
stack.1.A <- filter(all.tiles,A.or.B == "A",!is.na(Area.827)) %>% 
  select(Tile,Population,include, Status, Area.827, Area.1014,I.Growth.1014,Growth.1014,Area.113,I.Growth.113,Growth.113,Tray) %>%
    group_by(Population)
```

Make a new data frame with dates stacked on top of each other (easier to plot)
```{r}
new.827 <- select(stack.1.A,Tile,Population,Area.827,Tray) %>%  mutate(Growth=0) %>%mutate(I.Growth=0) %>% mutate(Day = "1")
colnames(new.827) <- c("Tile","Population","Area","Tray","Growth","I.Growth","Day")
new.1014 <- filter(stack.1.A,include !="n", !is.na(Area.1014),Growth.1014>0) %>%
    select(Tile,Population,Area.1014,Tray,Growth.1014,I.Growth.1014) %>%
    mutate(Day = "48")
colnames(new.1014) <-c("Tile","Population","Area","Tray","Growth","I.Growth","Day")
new.113 <- filter(stack.1.A,include!="n", !is.na(Area.113),Growth.113>0) %>%
    select(Tile,Population,Area.113,Tray,Growth.113,I.Growth.113) %>%  mutate(Day = "68")
colnames(new.113) <-c("Tile","Population","Area","Tray","Growth","I.Growth","Day")
stack.1.A.ex.byDay <- rbind(new.827,new.1014,new.113)
stack.1.A.ex.byDay <- group_by(stack.1.A.ex.byDay,Day,Population)
```
# Summarizing at different time points
```{r}
Shell.Size = summarise(stack.1.A.ex.byDay,mean.Area = mean(Area, na.rm = T),se.Area = std.error(Area,na.rm =T),mean.Igrowth = mean(I.Growth,na.rm=T), se.Igrowth = std.error(I.Growth,na.rm=T),mean.Growth=mean(Growth,na.rm=T),se.Growth=std.error(Growth,na.rm=T))
head(Shell.Size)
```
# Checking for normal distributions  
## Day 1 Area  

Plotting size distributions at Day 1.
```{r}
p.Day1 <- ggplot(filter(stack.1.A.ex.byDay,Day == 1), aes(x=Population, y=Area,fill=Population)) + 
  geom_violin(trim=FALSE) + scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9")) + geom_boxplot(width=0.1,fill="white") + labs(title="Area Day 1",y="Area (mm^2)")
p.Day1
```
Checking for normal distributions in Area.
```{r}
#Day 1
plot(density(filter(stack.1.A.ex.byDay,Day==1,Population=="Oyster Bay")$Area,na.rm = T),col="#56B4E9", main ="Day 1 distributions of Area")
lines(density(filter(stack.1.A.ex.byDay,Day==1,Population=="Dabob Bay")$Area,na.rm = T),col="#999999")
lines(density(filter(stack.1.A.ex.byDay,Day==1,Population=="Fidalgo Bay")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(stack.1.A.ex.byDay,Day==1,Population=="Oyster Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==1,Population=="Dabob Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==1,Population=="Fidalgo Bay")$Area)
```
Day 1 Area is not normal.

## Day 48 Area  
```{r,echo=FALSE}
plot(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Oyster Bay")$Area,na.rm = T),col="#56B4E9", main ="Day 48 distributions of Area",ylim=c(0,0.013))
lines(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Dabob Bay")$Area,na.rm = T),col="#999999")
lines(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Fidalgo Bay")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Oyster Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Dabob Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Fidalgo Bay")$Area)
```
Day 48 area is not normal, except for SS.  

## Day 68 Area   
```{r,echo=FALSE}
plot(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Oyster Bay")$Area,na.rm = T),col="#56B4E9", main ="Day 68 distributions of Area",ylim =c(0,0.009))
lines(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Dabob Bay")$Area,na.rm = T),col="#999999")
lines(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Fidalgo Bay")$Area,na.rm = T),col="#E69F00")

shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Oyster Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Dabob Bay")$Area)
shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Fidalgo Bay")$Area)
```
Shell area at day 68 does not have a normal distribution, except SS.  

## Growth rate
Checking for normal distribution of growth rate by Day 48
```{r,echo=FALSE}
plot(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Oyster Bay",Growth>0)$Growth,na.rm = T),col="#56B4E9", main ="Day 48 distributions of Growth Rate",ylim =c(0,0.75))
lines(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Dabob Bay",Growth>0)$Growth,na.rm = T),col="#999999")
lines(density(filter(stack.1.A.ex.byDay,Day==48,Population=="Fidalgo Bay",Growth>0)$Growth,na.rm = T),col="#E69F00")

shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Oyster Bay",Growth>0)$Growth)
shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Dabob Bay",Growth>0)$Growth)
shapiro.test(filter(stack.1.A.ex.byDay,Day==48,Population=="Fidalgo Bay",Growth>0)$Growth)
```
HC and NF not normal.
Checking for normal distribution of growth rate 48 - 68
```{r,echo=FALSE}
plot(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Oyster Bay")$Growth,na.rm = T),col="#56B4E9", main ="Day 48 distributions of Growth Rate",ylim =c(0,0.5))
lines(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Dabob Bay")$Growth,na.rm = T),col="#999999")
lines(density(filter(stack.1.A.ex.byDay,Day==68,Population=="Fidalgo Bay")$Growth,na.rm = T),col="#E69F00")

shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Oyster Bay")$Growth)
shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Dabob Bay")$Growth)
shapiro.test(filter(stack.1.A.ex.byDay,Day==68,Population=="Fidalgo Bay")$Growth)
```
HC and NF not normal.  

# Plotting size through time  
```{r}
Fig.Line.size <- ggplot(Shell.Size, aes(x=Day, y=mean.Area, group=Population)) + 
  geom_errorbar(aes(ymin=Shell.Size$mean.Area-Shell.Size$se.Area,ymax=Shell.Size$mean.Area+Shell.Size$se.Area,color=Population), width=.07,position = position_dodge(width = 0.05)) +
  geom_line(aes(color=Population) ,size = 1,position = position_dodge(width = 0.05)) +   
  geom_point(aes(shape=Population,color=Population), size = 4,position = position_dodge(width = 0.05))+
  xlab("Days") +
  ylab(expression(paste('Shell Area (',mm^2,')'))) +
  theme_bw(base_size = 16) + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 14), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Juvenile Shell Area") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 20, 
                                  hjust = 0))
Fig.Line.size + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
```

```{r}
Fig.Line.size <- ggplot(Shell.Size, aes(x=Day, y=mean.Growth, group=Population)) + 
  geom_errorbar(aes(ymin=Shell.Size$mean.Growth-Shell.Size$se.Growth,ymax=Shell.Size$mean.Growth+Shell.Size$se.Growth,color=Population), width=.07,position = position_dodge(width = 0.1)) +
  geom_line(aes(color=Population) ,size = 0.5,position = position_dodge(width = 0.1)) +   
  geom_point(aes(shape=Population,color=Population), size = 3,position = position_dodge(width = 0.1))+
  xlab("Days") +
  ylab(expression(paste("Shell Area Growth Rate (mm^2/day)"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Juvenile Shell Area Growth Rate") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.Line.size + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
```

Instantaneous growth- not used in paper, but here for reference.
```{r}
Fig.Line.size <- ggplot(Shell.Size, aes(x=Day, y=mean.Igrowth, group=Population)) + 
  geom_errorbar(aes(ymin=Shell.Size$mean.Igrowth-Shell.Size$se.Igrowth,ymax=Shell.Size$mean.Igrowth+Shell.Size$se.Igrowth,color=Population), width=.07,position = position_dodge(width = 0.1)) +
  geom_line(aes(color=Population) ,size = 0.5,position = position_dodge(width = 0.1)) +   
  geom_point(aes(shape=Population,color=Population), size = 3,position = position_dodge(width = 0.1))+
  xlab("Days") +
  ylab(expression(paste("Shell Area Instantaneous Growth"))) +
  theme_bw() + #Set the background color
  theme(axis.text.x = element_text(vjust = 1, hjust=1, size = 12), #Set the text angle
        axis.line = element_line(color = 'black'), #Set the axes color
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        plot.background=element_blank(),  #Set the plot background
        legend.key = element_blank(),  #remove legend background
        legend.position=c(.2, .7)) + #set legend location
  ggtitle("Juvenile Shell Area Instantaneous Growth") +
  theme(plot.title = element_text(face = 'bold', 
                                  size = 14, 
                                  hjust = 0))
Fig.Line.size + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
```

```{r}
SS <- filter(Shell.Size, Day != "1")
SS$Population <- factor(SS$Population,levels =c("Dabob Bay","Oyster Bay","Fidalgo Bay"))
Bar.size <- ggplot(SS, aes(x=Day, y=mean.Growth, fill=Population)) + 
  geom_bar(stat="identity", position=position_dodge()) +
  theme_bw() +
  geom_errorbar(aes(ymin=SS$mean.Growth-SS$se.Growth,ymax=SS$mean.Growth+SS$se.Growth), width=.07,position = position_dodge(0.9)) +
  scale_fill_manual(values=c("#999999", "#56B4E9","#E69F00" )) + 
  scale_x_discrete(labels = c("48" ="0 - 48","68" = "48 - 68"))
Bar.size
```

# Testing for differences in size   

## Day 1  
ANOVA of size at Day 1 to test if size differs accross populations at Day 1
```{r}
G1.D1 <- filter(stack.1.A.ex.byDay, Day==1)
area.D1 <- aov(log10(Area) ~ Population, data=G1.D1) #test the hypothesis relative size does not differ between treatments on Day 1
summary(area.D1)
```

Linear mixed models of size at each time point, with Population as a fixed effect and Tray as random effect.
Log-transformed area on Day 1
```{r}
D1 <- filter(stack.1.A.ex.byDay, Day == 1)
area.model = lmer(log10(Area) ~ Population + (1|Tray),data=D1,na.action = na.omit)
summary(area.model)
area.null <- lmer(log10(Area) ~ (1|Tray),data=D1,REML=FALSE)
area.model.R <- lmer(log10(Area) ~ Population + (1|Tray),data=D1,REML = F)
anova(area.null,area.model.R)
```
Not significant.

## Day 48  
Log-transformed shell area on Day 48.
```{r}
D48 <- filter(stack.1.A.ex.byDay, Day == 48, !(is.na(Area)))
area.model = lmer(log10(Area) ~ Population + (1|Tray),data=D48,na.action = na.omit)
summary(area.model)
area.null <- lmer(log10(Area) ~ (1|Tray),data=D48,REML=FALSE)
area.model.R <- lmer(log10(Area) ~ Population + (1|Tray),data=D48,REML = F)
anova(area.null,area.model.R)
```
p-value is 0.02188

Log-transformed growth rate, Day 1 to Day 48.
```{r,echo=FALSE}
area.model = lmer(log10(Growth) ~ Population + (1|Tray),data=D48,na.action = na.omit)
summary(area.model)
area.null <- lmer(log10(Growth) ~ (1|Tray),data=D48,REML=FALSE)
area.model.R <- lmer(log10(Growth) ~ Population + (1|Tray),data=D48,REML = F)
anova(area.null,area.model.R)
```
p-value = 0.01824

## Day 68  
Log-transformed Area Day 68
```{r}
D68 <- filter(stack.1.A.ex.byDay, Day == 68, !(is.na(Area)))
area.model = lmer(log10(Area) ~ Population + (1|Tray),data=D68,na.action = na.omit)
summary(area.model)
area.null <- lmer(log10(Area)~ (1|Tray),data=D68,REML=FALSE)
area.model.R <- lmer(log10(Area) ~ Population + (1|Tray),data=D68,REML = F)
anova(area.null,area.model.R)
```
p-value is 0.007936

Log-transformed growth rate, Day 48 to Day 68.
```{r,echo=FALSE}
area.model = lmer(log10(Growth) ~ Population + (1|Tray),data=D68,na.action =na.omit)
summary(area.model)
area.null <- lmer(log10(Growth) ~ (1|Tray),data=D68,REML=FALSE)
area.model.R <- lmer(log10(Growth) ~ Population + (1|Tray),data=D68,REML = F)
anova(area.null,area.model.R)
```
p-value is 0.001133

## Kruskal-Wallis tests  

Kruskal-Wallis test, with Nemenyi post-hoc test
Shell Area
```{r}
posthoc.kruskal.nemenyi.test(D1$Area,D1$Population,dist="Chisquare")
posthoc.kruskal.nemenyi.test(D48$Area,D48$Population,dist="Chisquare")
posthoc.kruskal.nemenyi.test(D68$Area,D68$Population,dist="Chisquare")
```
HC and NF are significantly different at Day 48 and 68

Growth Rate
```{r}
posthoc.kruskal.nemenyi.test(D48$Growth,D48$Population,dist="Chisquare")
posthoc.kruskal.nemenyi.test(D68$Growth,D68$Population,dist="Chisquare")
```
